Making Sequential Programs Deterministic

### 2019-04-06 randoop-case-study.tex
Add more explanation

\begin{itemize}
\item   (22\%)
%      8 constructors guarantee all instances of this class are @Det
  When every instance of a class is \<@Det>, \<@PolyDet> is equivalent to
  \<@Det>, but \theDeterminismChecker does not yet recognize this fact.
\item  (16\%)
%      6 https://github.com/t-rasmud/checker-framework/issues/96
  For a type that cannot be \<@OrderNonDet>, \<@PolyDet("up")> is
  equivalent to \<@PolyDet>.
\item (14\%)
%      5 can't specify receiver for anonymous class
  Java does not have syntax for specifying the type of an anonymous class.
\item (11\%)
%      4 actual type toString returns @PolyDet
  A variable is declared as \<Object> which has nondeterministic \<toString>,
  but at run time the value always has deterministic \<toString>.  For
  example, the run-time value is always an \<Integer> or a \<String>.
\item (5\%)
%      2 iterating over @OrderNonDet collection to modify another
  Iteration over an \<@OrderNonDet> collection in order to make another
  \<@OrderNonDet> collection, but the extracted elements have type
  \<@NonDet>.  For example, the following code is safe,
  \theDeterminismChecker issues a warning.  Variable \<elt> has type
  \<@NonDet>, so the call to \<add> does not typecheck.
\begin{Verbatim}
  void m(@OrderNonDet List<@Det String> input) {
    @OrderNonDet List<@Det String> output = new List<>();
    for (String elt : input) {
      output.add(elt);
    }
  }
\end{Verbatim}

>>>>

\begin{itemize}
\item   (22\%)
%      8 constructors guarantee all instances of this class are @Det
  When every instance of a class is \<@Det>, \<@PolyDet> is equivalent to
  \<@Det>, but \theDeterminismChecker does not yet recognize this fact.
\item  (16\%)
%      6 https://github.com/t-rasmud/checker-framework/issues/96
  For a type that cannot be \<@OrderNonDet>, \<@PolyDet("up")> is
  equivalent to \<@PolyDet>.
\item (14\%)
%      5 can't specify receiver for anonymous class
  Java does not have syntax for specifying the type of an anonymous class.
\item (11\%)
%      4 actual type toString returns @PolyDet
  A variable is declared as \<Object> which has nondeterministic \<toString>,
  but at run time the value always has deterministic \<toString>.  For
  example, the run-time value is always an \<Integer> or a \<String>.
\item (5\%)
%      2 iterating over @OrderNonDet collection to modify another
  Iteration over an \<@OrderNonDet> collection in order to make another
  \<@OrderNonDet> collection, but the extracted elements have type
  \<@NonDet>.  For example, the following code is safe, but
  \theDeterminismChecker issues a warning.  Variable \<elt> has type
  \<@NonDet>, so the call to \<add> does not typecheck.
\begin{Verbatim}
  void m(@OrderNonDet List<@Det String> input) {
    @OrderNonDet List<@Det String> output = new List<>();
    for (String elt : input) {  // elt has type @NonDet String
      output.add(elt);          // error: illegal argument
    }
  }
\end{Verbatim}
